\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-15 paper/background.tex
\scheme

Dark decoys are able to avoid these problems by splitting up the traffic between a registration session and a dark session \nikita{are these good terms?} (\cref{fig:dark-decoys}). The registration session is used to send a signal to the RS to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference. The dark session connects to a dark address that is not routed to any host; the RS instead acts as a remote endpoint for the entirety of the connection, starting with the TCP handshake. This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in \cref{XXX}.

\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the RS to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}. In principle dark decoys can use any of these mechanisms for registration, but n our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.

>>>>

\scheme is able to avoid these problems by splitting up the traffic between a registration session and a dark session \nikita{are these good terms?} (\cref{fig:dark-decoys}). The registration session is used to send a signal to the RS to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference. The dark session connects to a dark address that is not routed to any host; the RS instead acts as a remote endpoint for the entirety of the connection, starting with the TCP handshake. This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in \cref{XXX}.

\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the RS to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}. In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.

### 2019-02-15 paper/related.tex
Placement
\scheme

We first compare Dark Decoys with other Refraction Networking schemes and then discuss other related work.

@@

TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
decoy into staying silent, and allowing the station to respond instead. However,
as previously described, this trick comes at a cost: the decoy only stays silent
for a short timeout (typically 30-120 seconds), and limits the amount of data
the client can send before it responds. TapDance clients must keep connections
short and repeatedly reconnect to decoys, increasing overhead and potentially
alerting censors with this pattern. Dark Decoys addresses this issue and allows
clients to maintain long-lived connections to the dark decoy.

@@

Slitheen~\cite{slitheen16} focuses on addressing observability by replacing
data in packets sent by the legitimate decoy. Thus, even the packet timings and
sizes of a Slitheen connection match that of a legitimate decoy connection.
However, Slitheen also requires inline-blocking, and introduces a large overhead
as it has to wait for the subset of data-carrying packets from the decoy that
Slitheen can safely replace. We note that the Slitheen model of mimicry is
compatible with Dark Decoys, as we could use Slitheen as the application
protocol. Despite using a passive tap, our scheme is effectively inline to the
dark decoy (which won't otherwise respond).

@@

Dark Decoys allow a large amount of flexibility compared to previous schemes.
Because we have significant degrees of freedom in choosing the specific
application the dark decoy will mimic or talk, our scheme can combine the best
of existing Refraction Networking protocols to achieve high performance, be easy
to deploy, and
also be resistant to active attacks such as replaying or probing by the censor.
Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
their features, as compared to Dark Decoys.

@@

In practice, deployment of refraction networking has so far been at access, rather than transit ISPs~\cite{frolov2017isp}. This may be in part because a transit ISP has a large number of routers and points-of-presence, significantly raising the costs of deployment~\cite{devil-details}.\footnote{We
note that Gosain et al.~\cite{devil-details} use an estimate of \$885\,000 USD/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that cost only several thousand dollars.} Likewise, we expect Dark Decoys to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks. Depending on the size of the ISP, however, a censor may decide to block the entirety of its address space, which would incur smaller collateral damage than blocking all addresses seen by a transit ISP.

@@

Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor. Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this information secret is challenging; additonally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations. Dark Decoys further this goal by creating a large number of destinations out of the dark space. A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations. CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication. As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number. In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}

>>>>

We first compare \scheme with other Refraction Networking schemes and then discuss other related work.

@@

TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
decoy into staying silent, and allowing the station to respond instead. However,
as previously described, this trick comes at a cost: the decoy only stays silent
for a short timeout (typically 30-120 seconds), and limits the amount of data
the client can send before it responds. TapDance clients must keep connections
short and repeatedly reconnect to decoys, increasing overhead and potentially
alerting censors with this pattern. \scheme addresses this issue and allows
clients to maintain long-lived connections to the dark decoy.

@@

Slitheen~\cite{slitheen16} focuses on addressing observability by replacing
data in packets sent by the legitimate decoy. Thus, even the packet timings and
sizes of a Slitheen connection match that of a legitimate decoy connection.
However, Slitheen also requires inline-blocking, and introduces a large overhead
as it has to wait for the subset of data-carrying packets from the decoy that
Slitheen can safely replace. We note that the Slitheen model of mimicry is
compatible with \scheme, as we could use Slitheen as the application
protocol. Despite using a passive tap, our scheme is effectively inline to the
dark decoy (which won't otherwise respond).

@@

\scheme allow a large amount of flexibility compared to previous schemes.
Because we have significant degrees of freedom in choosing the specific
application the dark decoy will mimic or talk, our scheme can combine the best
of existing Refraction Networking protocols to achieve high performance, be easy
to deploy, and
also be resistant to active attacks such as replaying or probing by the censor.
Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
their features, as compared to \scheme.

@@

In practice, deployment of refraction networking has so far been at access, rather than transit ISPs~\cite{frolov2017isp}. This may be in part because a transit ISP has a large number of routers and points-of-presence, significantly raising the costs of deployment~\cite{devil-details}.\footnote{We
note that Gosain et al.~\cite{devil-details} use an estimate of \$885\,000 USD/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that cost only several thousand dollars.} Likewise, we expect \scheme to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks. Depending on the size of the ISP, however, a censor may decide to block the entirety of its address space, which would incur smaller collateral damage than blocking all addresses seen by a transit ISP.

@@

Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor. Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this information secret is challenging; additonally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations. \scheme further this goal by creating a large number of destinations out of the dark space. A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations. CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication. As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number. In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}
